---
title: "MA [46]15 Homework 4"
author: "**`[==[`** Xiaojing Yang **`]==]`**"
format: gfm
---


## Question 1


**`[==[`**
Download the [`hw4_cahmi_data.zip`](https://math.bu.edu/people/sussman/data/hw4_cahmi_data.zip) file and save or copy it to this directory and unzip it. (Make sure it is in a subdirectory named `data`. If you put it is in a different subdirectory you might accidentally commit it.)
Now modify the `q1` chunk below to create a new dataset called `cahc_df`.
Check that there are no errors when importing data. 

Check variables `age`, `fam_pov_lev`, `sex`, and `birth_weight_oz` for unusual values or unusually frequent values. (There is no "right" way to do this but provide some output showing that these are or are not present.)
Quickly comment on anything unusual.
**`]==]`**

My work is to perform a preliminary analysis of the Childhood and Adolescent Health conditions data downloaded from . 
This data set is derived from data that was collected in 2016 as part of the National Survey of Children's Health hosted by the [Data Resource Center for Child and Adolescent Health](https://www.childhealthdata.org/browse/archive-prior-year-nsch-and-ns-cshcn-data-resources/state-snapshot).
I read the file into a data set call `cahc_df`.
```{r q1}
suppressPackageStartupMessages(library(tidyverse))
```


## Question 2

**`[==[`**
Whether we view this data as being "tidy" depends on what we think of as an observation.
In order to ease the analysis across different health conditions, we want to view an observation as a distinct pair of child and potential health condition.
Use `pivot_longer` on all columns corresponding to one of the health conditions.
Specify the `cols` and then also use the parameters `names_pattern = "(.*)_(.*)$", names_to = c(".value", "condition")`.
(This is a slightly advanced use of `pivot_longer`. Look at the help for `pivot_longer` to better understand this.)
After you `pivot_longer` you should have 11 columns.
Save this to a new variable called `cahc_long`.

Verify by outputting empty tibbles that 

* `currently_has` is not `NA` only if `ever_had` is `"Yes"` and 
* `severity` is not `NA` only if `currently_has` is `"Yes"`.
**`]==]`**



## Question 3



**`[==[`**
Using the `cahc_long` data set, first count the number of conditions that each child currently has (which could be 0).
Then for each potential number of conditions, count how many children of each sex have that many conditions.
Make a bar chart showing the results.
The number of conditions will be on the x-axis and the number of children will be on the y-axis with the fill indicating the sex.
Comment on any differences you see between the two sexes.
**`]==]`**

```{r q3}

```



## Question 4

**`[==[`**
Again using the `cahc_long` data set, we're going going to create a table showing the proportion of children from different race categories who have different health conditions.
First, lump together any of the race categories with fewer than 5% of the total sample into an "Other" category.
Next, compute the proportion of children for each (remaining) race category that have each health condition.
Finally, use `pivot_wider` to create a table with rows corresponding to the health conditions and columns corresponding to the different race categories with the entries of the table giving the proportions.
(The resulting table will have dimensions 15x6.)

Comment on any major differences you observe between the different race categories.
**`]==]`**

```{r q4}
tibble(condition = letters[1:4], Purple = runif(4)) |>
  gt::gt() |> 
  gt::fmt_percent(-condition) |> 
  gt::as_raw_html()
```


